Supplement to: Optimal management of a stochastically varying population when policy adjustment is costly

### 2015-07-28 manuscripts/manuscript.Rmd
figure tidying
formatting for final submission

---
title: Optimal management of a stochastically varying population when policy adjustment is costly
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig (at) gmail.com
    footnote: Corresponding author
  - name: Michael Bode
    affiliation: melbourne
  - name: James N. Sanchirico
    affiliation: UCD
  - name: Jacob LaRiviere
    affiliation: UTKEcon
  - name: Alan Hastings
    affiliation: UCD
  - name: Paul R. Armsworth 
    affiliation: UTKEEB

address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research,
      110 Shaffer Rd,
      Santa Cruz, CA 95050, USA 
  - code: UCD
    address: Department of Environmental Science and Policy, University of California, Davis
  - code: melbourne
    address: School of Botany, University of Melbourne, Australia 
  - code: UTKEEB
    address: Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville
  - code: UTKEcon
    address: Department of Economics, University of Tennessee, Knoxville

@@

layout: review,12pt,author-year,titlepage
linenumbers: true
bibliography: components/references.bib
csl: components/ecology.csl
documentclass: components/elsarticle
geometry: [verbose,letterpaper,tmargin=2.54cm,bmargin=2.54cm,l
margin=2.54cm,rmargin=2.54cm]

@@

R code for implementing the dynamic programming algorithm in this context is
provided as a supplementary R package to the paper, ([github.com/cboettig/pdg_control](https://github.com/cboettig/pdg_control)), along with scripts for replicating 
the analyses presented here. To address concerns about computational reproducibility [@Boettiger2015],
a Docker container image of the software environment is also provided.

@@

Figure 4 shows these qualitative patterns still hold at when the models are calibrated 
to a range of different reductions in NPV, from 0% to 30%, though naturally the magnitude
of the differences is greatest when the penalty is larger.

@@

```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue).  All values are relative to the cost free adjustment optimum, $NPV_0$.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.Supplementary Figure S6 shows how the magnitude of this effect changes with the size of the reduction to $NPV$.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}

>>>>

---
title: Optimal management of a stochastically varying population when policy adjustment is costly
author: 
  - name: Carl Boettiger
    affiliation: UCB 
    email: cboettig (at) berkeley.edu 
    footnote: Corresponding author
  - name: Michael Bode
    affiliation: melbourne
  - name: James N. Sanchirico
    affiliation: UCD
  - name: Jacob LaRiviere
    affiliation: UTKEcon
  - name: Alan Hastings
    affiliation: UCD
  - name: Paul R. Armsworth 
    affiliation: UTKEEB

address: 
  - code: UCB
    address: | 
      Department of Environmental Science, Policy and Management,
      University of California, Berkeley,
      130 Mulford Hall \#3114,
      Berkeley, CA 94720-3114, USA
  - code: UCD
    address: Department of Environmental Science and Policy, University of California, Davis
  - code: melbourne
    address: School of Botany, University of Melbourne, Australia 
  - code: UTKEEB
    address: Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville
  - code: UTKEcon
    address: Department of Economics, University of Tennessee, Knoxville

@@

layout: review,12pt,author-year,titlepage
linenumbers: true
bibliography: components/references.bib
csl: components/ecology.csl
documentclass: components/elsarticle
geometry: [verbose,letterpaper,tmargin=2.54cm,bmargin=2.54cm,l
margin=2.54cm,rmargin=2.54cm]
endfloat: true
doublespacing: true

@@

R code for implementing the dynamic programming algorithm in this context is
provided as a supplementary R package to the paper, ([github.com/cboettig/pdg_control](https://github.com/cboettig/pdg_control), @zenodo_copy), along with scripts for replicating 
the analyses presented here. To address concerns about computational reproducibility [@Boettiger2015],
a Docker container image of the software environment is also provided.

@@

Figure 4 shows these qualitative patterns still hold at when the models are calibrated 
to a range of different reductions in NPV, from 0% to 30%, though naturally the magnitude
of the differences is greatest when the penalty is larger. Note that the supplementary material provide
further evidence that these patterns are independent of the exact reduction shown by providing
results analogous to Figure 3 (A8, A9) and Figure 5 (A10, A11), and Figure 6 (A6).

@@

```{r Figure_6, fig.cap="Relative cost of ignoring adjustment costs when they are present ('ignoring', red) vs assuming the adjustment costs when they are absent ('assuming', blue).  All values are relative to the cost free adjustment optimum, $NPV_0$.  In each case, it is less costly to assume adjustment costs are present when they are not than it is to ignore them when they are present.Supplementary Figure A6 shows how the magnitude of this effect changes with the size of the reduction to $NPV$.", dev=c("pdf", "svg", "png"), fig.width=7, cache=FALSE}

### 2015-07-28 manuscripts/supplement.Rmd
formatting for final submission

---
title: "Supplement to: Optimal management of a stochastically varying population when policy adjustment is costly"
author: 
  - name: Carl Boettiger
    affiliation: cstar
    email: cboettig (at) gmail.com
    footnote: Corresponding author
  - name: Michael Bode
    affiliation: melbourne
  - name: James Sanchirico
    affiliation: UCD
  - name: Jacob LaRiviere
    affiliation: UTKEcon
  - name: Alan Hastings
    affiliation: UCD
  - name: Paul R. Armsworth 
    affiliation: UTKEEB

address: 
  - code: cstar
    address: | 
      Center for Stock Assessment Research,
      110 Shaffer Rd,
      Santa Cruz, CA 95050, USA 
  - code: UCD
    address: Department of Environmental Science and Policy, University of California, Davis
  - code: melbourne
    address: School of Botany, University of Melbourne, Australia 
  - code: UTKEEB
    address: Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville
  - code: UTKEcon
    address: Department of Economics, University of Tennessee, Knoxville

layout: review,12pt
linenumbers: true

@@

\makeatletter
\renewcommand\appendix{\par
  \setcounter{section}{0}%
  \setcounter{subsection}{0}%
  \setcounter{equation}{0}%
  \setcounter{table}{0}%------------ << add
  \setcounter{figure}{0}%----------- << add
  \gdef\theequation{S\arabic{equation}}%
  \gdef\thefigure{S\arabic{figure}}%
  \gdef\thesection{S@section}%
  \@addtoreset{equation}{section}%
  \@addtoreset{table}{section}%----- << add
  \@addtoreset{figure}{section}%---- << add
}
\makeatother

@@

All code and data used in this analysis can be found under the project's GitHub repository: [https://github.com/cboettig/pdg_control](https://github.com/cboettig/pdg_control). A snapshot of this repository representing the precise versions of the code used in this analysis has been permanently archived in the scientific software and data repository Zenodo, managed by CERN; and should be referenced or cited using its assigned digital object identifier, doi:xxx.  (This DOI is also clearly linked from the GitHub repository).

@@

>>>>

---
title: "Supplement to: Optimal management of a stochastically varying population when policy adjustment is costly"
author: 
  - name: Carl Boettiger
    affiliation: UCB 
    email: cboettig (at) berkeley.edu 
    footnote: Corresponding author
  - name: Michael Bode
    affiliation: melbourne
  - name: James N. Sanchirico
    affiliation: UCD
  - name: Jacob LaRiviere
    affiliation: UTKEcon
  - name: Alan Hastings
    affiliation: UCD
  - name: Paul R. Armsworth 
    affiliation: UTKEEB

address: 
  - code: UCB
    address: | 
      Department of Environmental Science, Policy and Management,
      University of California, Berkeley,
      130 Mulford Hall \#3114,
      Berkeley, CA 94720-3114, USA
  - code: UCD
    address: Department of Environmental Science and Policy, University of California, Davis
  - code: melbourne
    address: School of Botany, University of Melbourne, Australia 
  - code: UTKEEB
    address: Department of Ecology and Evolutionary Biology, University of Tennessee, Knoxville
  - code: UTKEcon
    address: Department of Economics, University of Tennessee, Knoxville

layout: preprint,12pt
linenumbers: false
endfloat: false

@@

\makeatletter
\renewcommand\appendix{\par
  \setcounter{section}{0}%
  \setcounter{subsection}{0}%
  \setcounter{equation}{0}%
  \setcounter{table}{0}%------------ << add
  \setcounter{figure}{0}%----------- << add
  \gdef\theequation{A\arabic{equation}}%
  \gdef\thefigure{A\arabic{figure}}%
  \gdef\thesection{A@section}%
  \@addtoreset{equation}{section}%
  \@addtoreset{table}{section}%----- << add
  \@addtoreset{figure}{section}%---- << add
}
\makeatother

@@

All code and data used in this analysis can be found under the project's GitHub repository: [https://github.com/cboettig/pdg_control](https://github.com/cboettig/pdg_control). A snapshot of this repository representing the precise versions of the code used in this analysis has been permanently archived in the scientific software and data repository Zenodo, managed by CERN; and should be referenced or cited using its assigned digital object identifier, doi:10.5281/zenodo.21416  (This DOI is also clearly linked from the GitHub repository).

@@

\newpage

# References
